### 2015-02-17 Paper1 (copy)/paper1B.tex
Work machine updates. Better .gitignore
huh

% Please keep the abstract between 250 and 300 words
\section*{Abstract}
Our actions often do not match our intentions when there are external disturbances such as turbulence. We derived a novel modeling approach for determining this motor intent from targeted reaching motions that are disturbed by an unexpected force. First, we demonstrated how to mathematically invert both feedforward (predictive) and feedback controls to obtain an intended trajectory. We next examined the model's sensitivity to a realistic range of parameter uncertainties, and found that the expected inaccuracy due to all possible parameter mis-estimations was less than typical movement-to-movement variations seen when humans reach to similar targets. The largest sensitivity arose mainly from uncertainty in joint stiffnesses. Humans cannot change their intent until they acquire sensory feedback, therefore we tested the hypothesis that a straight-line intent should be evident for at least the first 120 ms following the onset of a disturbance. As expected, the intended trajectory showed no change from undisturbed reaching for more than 300 ms after the disturbance onset. Beyond this point, however, we detected a change in intent, surprisingly even when the hand is already near the target. Knowing such an intent signal is broadly applicable: enhanced human-machine interaction, the study of impaired intent in neural disorders, the real-time determination (and manipulation) of error in training, and complex systems that embody planning such as brain machine interfaces, team sports, crowds, or swarms. In addition, observing intent as it changes might act as a window into the mechanisms of planning, correction, and learning.

@@

\subsection*{Human Subjects}
The human data trajectories analyzed here are drawn from four subjects who gave informed consent in accordance with Northwestern University Institutional Review Board, which specifically approved this study and follows the principles expressed in the Declaration of Helsinki. Two male and two female right-handed subjects (ages 24 to 30) performed the reaches with their right arm and were not compensated. Subjects' arm segment lengths were directly measured \textit{in situ} while body mass was self-reported.

@@

% Do NOT remove this, even if you are not including acknowledgments.
\section*{Acknowledgments}
Research supported by US NIH NINDS1 R01 NS053606.  We thank Felix Huang, Yazan Majeed, Jagan Jimmy, Christine Massie, Tejas Madhavan, and Mohi Ahmed for their review of our preliminary manuscripts. We also thank the community  of the Robotics Lab at the Rehabilitation Institute of Chicago for critical commentary during the genesis of this paper and the work leading up to it.

>>>>

% Please keep the abstract between 250 and 300 words
\section*{Abstract}
Our actions often do not match our intentions when there are external disturbances such as turbulence. We derived a novel modeling approach for determining this motor intent from targeted reaching motions that are disturbed by an unexpected force. First, we demonstrated how to mathematically invert both feedforward (predictive) and feedback controls to obtain an intended trajectory. We next examined the model's sensitivity to a realistic range of parameter uncertainties, and found that the expected inaccuracy due to all possible parameter mis-estimations was less than typical movement-to-movement variations seen when humans reach to similar targets. The largest sensitivity arose mainly from uncertainty in joint stiffnesses. Humans cannot change their intent until they acquire sensory feedback, therefore we tested the hypothesis that a straight-line intent should be evident for at least the first 120 milliseconds following the onset of a disturbance. As expected, the intended trajectory showed no change from undisturbed reaching for more than 300 milliseconds after the disturbance onset. Beyond this point, however, we detected a change in intent, surprisingly even when the hand is already near the target. Knowing such an intent signal is broadly applicable: enhanced human-machine interaction, the study of impaired intent in neural disorders, the real-time determination (and manipulation) of error in training, and complex systems that embody planning such as brain machine interfaces, team sports, crowds, or swarms. In addition, observing intent as it changes might act as a window into the mechanisms of planning, correction, and learning.

@@

\subsection*{Human Subjects}
The human data trajectories analyzed here are drawn from four subjects who gave written informed consent after reading a consent form approved by Northwestern University Institutional Review Board, which specifically approved this study following the principles expressed in the Declaration of Helsinki. Two male and two female right-handed subjects (ages 24 to 30) performed the reaches with their right arm and were not compensated. Subjects' arm segment lengths were directly measured \textit{in situ} while body mass was self-reported.

@@

% Do NOT remove this, even if you are not including acknowledgments.
\section*{Acknowledgments}
Research supported by US NIH NINDS1 R01 NS053606.  We thank Felix Huang, Jagan Jimmy, Christine Massie, Tejas Madhavan, and Mohi Ahmed for their review of preliminary manuscript. We also thank the community  of the Robotics Lab at the Rehabilitation Institute of Chicago for critical commentary during the genesis of this paper and the work leading up to it.
